### 2022-05-29 article.tex
Fix refs
Done most

There are multiple websites for hosting code, with GitHub,
and GitLab being the most well-known.
GitHub is the most commonly used website to host code in general,
with millions of users.
GitHub users can create dedicated websites (called 'repositories')
to upload code. GitHub hosts that uploaded by and provides
a user interface for every visiter of such a website.
An example from the author is the website \cite{bbbq_article_issue_157},
that hosts part of the code for the paper \cite{bilderbeek2022transmembrane}.

@@

A commit history helps to assess the honesty 
in the reporting of the code. 
Ideally, the full version history of the code 
has been generated, by hosting the code directly at its inception.
However, in some repositories, only the final version of the code has been
posted, which means all historical information is lost.
From a code history, it can be observed, for example, 
how much statistical tests have really/actually been done 
and see if all are reported:
not reporting a statistical tests is considered a Dubious Research Practice.

@@

@@

@@

\paragraph{Code is hard to manage}

Unlike English, code is fragile in standing the test of time.
Containers can alleviate this.
Code has a limited lifetime.

\paragraph{Runnable code has other important features}

 * Reproduce an experiment
 * Code can teach the user, see babette
 * Build upon an experiment

@@

Stuff

>>>>

There are multiple websites for hosting code, with GitHub,
and GitLab being the most well-known.
GitHub is the most commonly used website to host code in general,
with millions of users.
GitHub users can create dedicated websites (called 'repositories')
to upload code. GitHub hosts that uploaded by and provides
a user interface for every visiter of such a website.
An example from the author is the website \cite{bbbqarticleissue157},
that hosts part of the code for the paper \cite{bilderbeek2022transmembrane}.

@@

A commit history helps to assess the honesty 
in the reporting of the code. 
Ideally, the full version history of the code 
has been generated, by hosting the code directly at its inception.
However, in some repositories, only the final version of the code has been
posted, which means all historical information is lost.
From a code history, it can be observed, for example, 
how much statistical tests have really/actually been done 
and see if all are reported:
not reporting a statistical tests is considered a Dubious Research Practice 
\richel{REF}, as this allows dishonest reporting of p-value hacking.

@@

Some code hosts, among others, GitHub, 
allows the researcher to start software scripts when uploading a new version.
To determine the reproducibility of the code, one such script should
run the code (on trivial data) to verify if the code works at all.
If the functionality of the code is lost, the researcher
can immediatly see which small change was the cause of this.
A more sophisticated check for the code's correctness is
to run units tests and determine the percentage of code that has been
tested, which is called the code coverage. The higher the code coverage,
the \richel{ref}.

@@

Most code hosts, among others, GitHub and GitLab,
automatically keep track of certain metrics.
One such metric is the amount of code each contributor has made.
In that way, authors involved in the writing of the software
are honestly acknowledged.

\paragraph{A reader can contact the author}

A feature that gets too few attention is that code hosts
allow users to post bug reports and/or ask questions.
This allows other researchers to assess the health
of the code.

\paragraph{The problems with hosted code}

Albeith hosted code is vastly superior over raw code
in case of reproduciblity and correctness,
there are some problems with hosted code as well.
The most important one is that hosted code needs maintanance:
the libraries that are used by an experiment
will change over time, inevitably causing the experiment to fail
over time. This process is called bit rot and is a fundamental
problem \richel{ref}. A solution that has more 
longevity is to publishing the code installed in a virtual environment,
as described below.

A lesser problem, which is only a problem to some, is, that
the author of the code can be contacted and that bugs can be reported.
It can be argued that no energy should be wasted on published code.
This is however, a rather selfish point: a bug should be reported and
given proper attention, for the sake of the correctness of the 
results published.

@@

The most reproducible way of submitting the code of an experiment,
is by providing the code and all it needs 
installed in a virtual container.
Virtualization allows one to provide a standard environment,
that can be used on any other computer.
The best known examples of container software are Docker and Singularity,
where the latter is the only viable option to be able to run
an experiment on a high performance computing (HPC) environment,
such as a computer cluster.

\paragraph{Containers allow for runnable code, for longer periods of time}

Unlike English, code is fragile in standing the test of time.
Containers can alleviate this, as these can be created at a point
in time and then run later. Because the container is stand-alone,
all libraries the code depends on remain in their current/old state.
As with hosted code, an experiment may not run with newer versions
of libraries anymore, but a containerized experiment can run regardless, if
one refrains from updating.

Ideally, to re-do an experiment, one would need a one-liner to a container,
for example, \verb|singularity run my_experiment.sif run|.

\paragraph{Runnable code can precisely reproduce an experiment}

Containers allow a computation experiment to be highly reproducible:
given the same data, an experiment put into a container will give
the same results on different platforms, at least in theory.
In practice, differences may be observed when peripheral factors
are different, such as the random numbers as generated by an operating
system, or data that is downloaded from additional online sources.

\paragraph{Runnable code allows others to re-use an experiment}

Containers allow a computation experiment to be highly re-usable,
as any scientist can work with it and tweak code.

\paragraph{The problems with runnable code}

There are some problems with providing a container with a runnable container.
First, a container is several gigabytes and need to be stored somewhere
online. Ideally, this would be at Syslabs, as that one is free, yet
there is a limit of 15 Gb. Also, Sylabs does not allow much metadata to
be entered, such as the URL of the article, nor the URL of hosted code.
Also, journals do not request hosted code, nor runnable code.

\paragraph{Runnable code is the pinnacle of reproducible research}

When research truly needs to be reproducible, putting the code 
of an experiment into a container is a good solution, as it 
can stand the test of time well. Rewarding this, however, is not
done yet by journals.

@@
